s.function

### 2025-01-23 src/s_la_per_firm_corrected.Rmd
lad curves

>>>>

## One line plot for all LAD

```{r}
a.la <- tibble()
all.la <- df %>% 
  filter(ladcd != "NA") %>% 
  distinct(ladcd) %>% 
  #slice_head(n=100) %>% 
  simplify2array()

for (i in all.la){
  data <- df %>% filter(ladcd==i) %>%
    dplyr::select(year, ladcd, n)

  tryCatch(model <- (nls(n ~ SSlogis(year, Asym, xmid, scal), 
                         data = data, 
                         control = nls.control(maxiter = 1000))), error=function(e) NULL)

  model.name <- paste0("model.", i)

  assign(model.name, model)

  tryCatch(b.la <- tidy(model), error=function(e) NULL)

  tryCatch(a.la <-rbind(a.la, b.la), error=function(e) NULL)
}

# plot
path.out <- paste0(path, "/outputs/s/lad_per_firm_all.png")

ggplot(pred %>% 
              left_join(a.la), 
            aes(x = year, y = n, color = fast, group = ladcd)) +
  geom_line(aes(y = prednls), size = .1, alpha = .7) +
  scale_x_continuous(NULL, labels = as.character(df$year), breaks = df$year) +
  #geom_vline(xintercept = xmid.uk) +
  ylab("N. of websites / per firm") + 
  labs(color = "Website \ndiffusion speed") +
  theme(legend.position=c(.9,.15)) +
  scale_color_manual(values = c("fast" = "purple",
                                "slow"="orange"),
                     limits = force) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        panel.grid.minor = element_blank()) +
  geom_vline(xintercept = xmid.uk, colour="grey30", linetype="dashed")

ggsave(filename = path.out, bg="white")
```
